---
title: "Exam 2 PDF"
author: "RLong"
date: "6/26/2020"
output: word_document

---


clear the environment
```{r}
rm(list=ls(all=TRUE))
```

new project, select working directory

load the inequality dataset and save the data frame
```{r}
library(rio)
inequality_data = import("inequality.xlsx")
```
#this is a cross sectional dataset because it is analyzes data from one year, 2015.
```{r}
head(inequality_data)
summary(inequality_data) #see the year column in the console
```
#subset command to provide the gini scores for denmark and sweden

subset(inequality_data$inequality_gini, "Denmark")
subset(inequality_data$inequality_gini, "Sweden")

#6 it is better to have low inequality_gini scores, as seen with Denmark and Sweden.

#Taking a quick peak at the data frame
```{r}
head(inequality_data)
```
#writing a function called accent.remove to remove the accent on Belarus
```{r}
inequality_data$country[inequality_data$country=="Belarús"] = "Belarus"
```
#head command again to show that I removed the accent.
```{r}
head(inequality_data)
```
#sort the data by lowest inequality_gini scores
```{r}
inequality_data = inequality_data[order(inequality_data$inequality_gini),]
```
#mean of the inequality_gini score
```{r}
mean(inequality_data$inequality_gini, na.rm =TRUE)
```
#creating dummy variables 
```{r}
low_inequality <- ifelse(inequality_data$inequality_gini < 36.81, 1, 0)
high_inequality <- ifelse(inequality_data$inequality_gini > 36.81, 1, 0)
```
#run a cross tab using the dummy variables
```{r}
library(doBy)
summaryBy(low_inequality ~ high_inequality, data=inequality_data,  
          FUN = c(mean, length))
```
#write a for loop that prints three actors
```{r}
people_reduce <- c('The World Bank', 'African Development Bank', 'Bill and Melinda Gates Foundation')
for ( i in people_reduce){
  print(i)
}  
```
#the variable that is correlated with inequality is poverty. Multidimensional poverty headcount. I picked it because it has the Gini index and says Poverty and equity data

#import the variable into R
```{r}
library(WDI)
multi_poverty=WDI(country = "all",
                  indicator = c("SI.POV.MDIM"), # indicator from web
                  start = 2015, end = 2015, extra = FALSE, cache = NULL)
```
#merge the new variable into other dataset
```{r}
library(tidyverse)
merged_df = left_join(x=inequality_data,
                        y=multi_poverty,
                        by=c("country", "year"))
```
#remove the missing data on the basis of inequality_gini
```{r}
merged_df<- na.omit(merged_df, select=c("inequality_gini", "multi_poverty"))
```
#keeping the data with inequality_gini scores greater than 30
```{r}
library(dplyr)
data_greater_30 <- 
  merged_df %>%
  dplyr::filter(!(merged_df$inequality_gini< 30))
```
#count how many countries have the sequence "ai" in their name
```{r}
grep("ai", data_greater_30)
```
#apply family to take the sum of inequality_gini
```{r}
data_greater_30 <- sapply(data_greater_30$inequality_gini, sum)
```
#label your variables
```{r}
library(labelled)
var_label(merged_df) <- list(`country` = "Country",
                               `year` = "year",
                               `inequality_gini` = "Gini Index for Inequality",
                               `SI.POV.MDIM` = "MultiDimensional Poverty Measure")
```
#save the labelled data frame as a Stata
```{r}
library(rio)
```
export(merged_df, file = "final_data.dta")

[link to the git hub repo](https://github.com/RolongAlong/exam2.git)

ssh key
git@github.com:RolongAlong/exam2.git
